\documentclass{toospoint}

%% Override the consulting-agreement header from the shared class
\fancyhead[C]{%
  \sffamily\small\color{TPGray}%
  \textbf{\color{TPDark}OPERATING AGREEMENT}\\[2pt]
  \textcolor{TPTeal}{ToosPoint LLC}%
}

\hypersetup{
  pdftitle={ToosPoint LLC Operating Agreement},
  pdfauthor={ToosPoint LLC}
}

\begin{document}

%% ── Cover Page ────────────────────────────────────────────────────────────────
\contracttitle
  {OPERATING AGREEMENT}
  {ToosPoint LLC}
  {\today}

%% ── Preamble ──────────────────────────────────────────────────────────────────
\begin{clausebox}
\sffamily\small
This \textbf{Operating Agreement} (the ``Agreement'') of \textbf{ToosPoint
LLC} (the ``Company''), a single-member limited liability company organized
under the laws of the State of California, is entered into and effective as
of \today\ by \textbf{Sahar Vojoodi}, as the sole member (the ``Member'').
\end{clausebox}

\vspace{10pt}

%% ── Section 1 ─────────────────────────────────────────────────────────────────
\section{Company}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item \textbf{Name:} ToosPoint LLC
  \item \textbf{State of Formation:} California
  \item \textbf{Date of Formation:} June 5, 2026
  \item \textbf{California Secretary of State File No.:} B20260265785
  \item \textbf{Principal Office:} 27446 Hyatt Ct, Laguna Niguel, CA 92677-3701
\end{itemize}

%% ── Section 2 ─────────────────────────────────────────────────────────────────
\section{Sole Member}

The Company has one member: \textbf{Sahar Vojoodi} (the ``Member'').

%% ── Section 3 ─────────────────────────────────────────────────────────────────
\section{Ownership}

The Member owns \textbf{100\% (one hundred percent)} of the membership
interest in the Company. No other person or entity has any ownership,
voting, or economic interest in the Company unless and until this Agreement
is amended in writing by the Member.

%% ── Section 4 ─────────────────────────────────────────────────────────────────
\section{Management}

The Company is \textbf{member-managed}, managed solely by \textbf{Sahar
Vojoodi}. The Member has full and exclusive authority to manage the
business and affairs of the Company and to make all decisions on its behalf.

%% ── Section 5 ─────────────────────────────────────────────────────────────────
\section{Purpose}

The purpose of the Company is to engage in \textbf{business consulting
services} and any other lawful business activity for which a limited
liability company may be organized under the laws of the State of
California.

%% ── Section 6 ─────────────────────────────────────────────────────────────────
\section{Capital Contributions}

The Member has made an initial capital contribution to the Company as
reflected in the Company's books and records. The Member may, but is not
obligated to, make additional capital contributions from time to time at
the Member's sole discretion.

%% ── Section 7 ─────────────────────────────────────────────────────────────────
\section{Banking and Separation of Funds}

The Company shall maintain one or more bank accounts in the Company's name,
separate and distinct from any personal accounts of the Member.
\textbf{Business funds and personal funds shall be kept strictly separate at
all times.} The Member shall not commingle Company funds with personal
funds. All Company income shall be deposited into, and all Company
expenses shall be paid from, the Company's accounts.

\begin{clausebox}
\sffamily\footnotesize\color{TPGray}
\textbf{Note:} Maintaining strict separation of business and personal
finances is essential to preserving the limited liability protection of
the LLC structure. Commingling of funds may result in loss of liability
protection (``piercing the corporate veil'').
\end{clausebox}

%% ── Section 8 ─────────────────────────────────────────────────────────────────
\section{Authority of the Member}

\textbf{Sahar Vojoodi}, as the sole Member, has full and unilateral
authority to act on behalf of the Company, including but not limited to:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Opening, maintaining, and closing bank accounts, merchant accounts,
        and payment-processing accounts in the Company's name
  \item Signing checks, wires, ACH authorizations, and other payment
        instruments on behalf of the Company
  \item Negotiating, executing, and terminating contracts, agreements,
        leases, and other binding instruments on behalf of the Company
  \item Hiring, engaging, and terminating employees, contractors, and
        professional advisors
  \item Filing tax returns and other regulatory filings on behalf of
        the Company
  \item Taking any other action necessary or appropriate to conduct the
        business of the Company
\end{itemize}

Any third party, including banks and counterparties, may rely on the
Member's authority as set forth herein without further inquiry or
additional documentation.

%% ── Section 9 ─────────────────────────────────────────────────────────────────
\section{Profits, Losses, and Distributions}

All profits and losses of the Company shall be \textbf{allocated entirely
to the sole Member}. Distributions of cash or other property may be made
to the Member at such times and in such amounts as the Member shall
determine in the Member's sole discretion.

%% ── Section 10 ────────────────────────────────────────────────────────────────
\section{Tax Treatment}

The Company is a single-member limited liability company and is, by
default, treated as a \textbf{disregarded entity} for U.S. federal income
tax purposes. The Company's income, deductions, and credits are reported
on the Member's individual federal income tax return (Form 1040,
Schedule C). The Company shall also file California Form 568 and pay the
annual \$800 California LLC franchise tax (Form 3522) and applicable
LLC fee.

%% ── Section 11 ────────────────────────────────────────────────────────────────
\section{Indemnification}

To the fullest extent permitted by California law, the Company shall
indemnify the Member against any claim, liability, loss, or expense
arising out of any action taken in good faith on behalf of the Company.

%% ── Section 12 ────────────────────────────────────────────────────────────────
\section{Dissolution}

The Company shall be dissolved upon (a) the written election of the
Member, or (b) any event requiring dissolution under California law.
Upon dissolution, the Company's affairs shall be wound up and its assets
distributed in accordance with California law and this Agreement.

%% ── Section 13 ────────────────────────────────────────────────────────────────
\section{Amendment}

This Agreement may be amended only by a written instrument signed by the
Member.

%% ── Section 14 ────────────────────────────────────────────────────────────────
\section{Governing Law}

This Agreement shall be governed by and construed in accordance with the
laws of the State of California, without regard to its conflict of laws
principles.

%% ── Signature Block ───────────────────────────────────────────────────────────
\vspace{28pt}

\begin{center}
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}\\[6pt]
  {\sffamily\bfseries\color{TPDark}IN WITNESS WHEREOF}\\[4pt]
  {\sffamily\small\color{TPGray}the undersigned, being the sole Member of ToosPoint LLC, has executed this Operating Agreement as of the date set forth above.}\\[6pt]
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}
\end{center}

\vspace{20pt}

\noindent
\signatureblock{Sahar Vojoodi}{Sole Member, ToosPoint LLC}

\vspace{32pt}

\begin{mdframed}[
  linecolor=TPBorder,
  linewidth=1pt,
  roundcorner=4pt,
  backgroundcolor=TPLight,
  innerleftmargin=14pt,
  innerrightmargin=14pt,
  innertopmargin=10pt,
  innerbottommargin=10pt
]
\sffamily\footnotesize\color{TPGray}
\textbf{INTERNAL CORPORATE RECORD:} This Operating Agreement is the
governing document of ToosPoint LLC. The original signed copy should be
retained with the Company's corporate records. A copy may be provided to
banks, tax authorities, and other parties as required to conduct the
Company's business.
\end{mdframed}

\end{document}
