\documentclass{toospoint}

\begin{document}

%% ── Cover Page ────────────────────────────────────────────────────────────────
\contracttitle
  {CONSULTING AGREEMENT}
  {ToosPoint Consulting \quad×\quad iCall International}
  {\today}

%% ── Preamble ──────────────────────────────────────────────────────────────────
\begin{clausebox}
\sffamily\small
This \textbf{Consulting Agreement} (the ``Agreement'') is entered into between
\textbf{ToosPoint Consulting} (``Consultant'') and \textbf{iCall International}
(``Company''). The parties agree to the terms and conditions set forth herein.
\end{clausebox}

\vspace{10pt}

%% ── Section 1 ─────────────────────────────────────────────────────────────────
\section{Scope of Services}

Consultant will provide services related to the following areas on behalf of the Company:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Direct client acquisition and pipeline development
  \item Sales strategy design and execution
  \item Outreach programs and campaign management
  \item RFP identification, preparation, and submission
  \item Related consulting and execution support as mutually agreed
\end{itemize}

%% ── Section 2 ─────────────────────────────────────────────────────────────────
\section{Compensation}

Company agrees to pay Consultant an \textbf{hourly rate of \$95 USD per hour} for
all services rendered under this Agreement. Consultant shall submit a monthly
invoice itemizing hours worked and services performed. Payment is due
\textbf{Net~15} from the invoice date.

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item All hours are billed in increments rounded to the nearest quarter hour
  \item No commission, revenue share, or success fee is payable under this
        Agreement; compensation is strictly hourly
\end{itemize}

\begin{clausebox}
\sffamily\footnotesize\color{TPGray}
\textbf{Note:} Invoices are issued at the beginning of each month for hours
worked in the prior month and are payable Net~15.
\end{clausebox}

%% ── Section 3 ─────────────────────────────────────────────────────────────────
\section{Maximum Monthly Hours}

The Consultant's services under this Agreement shall not exceed \textbf{forty~(40)
hours per calendar month} unless otherwise mutually agreed upon in writing by both
parties in advance. Any additional hours beyond the monthly maximum must be
approved in writing prior to performance of such services.

%% ── Section 4 ─────────────────────────────────────────────────────────────────
\section{Term and Termination}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item This Agreement will begin on the agreed effective date and continue on a
        \textbf{month-to-month} basis until terminated.
  \item Either party may terminate this Agreement with \textbf{30~days written notice}.
  \item Upon termination, Company shall pay Consultant for all hours worked
        through the effective termination date.
\end{itemize}

%% ── Section 5 ─────────────────────────────────────────────────────────────────
\section{Independent Contractor}

Consultant is an \textbf{independent contractor} and not an employee, agent, or
partner of the Company. Consultant retains sole responsibility for all taxes, benefits,
and obligations arising from Consultant's business operations. Nothing in this Agreement
shall be construed to create an employment, partnership, or joint-venture relationship.

%% ── Section 6 ─────────────────────────────────────────────────────────────────
\section{Confidentiality}

Both parties agree to maintain the confidentiality of each other's proprietary
information, trade secrets, client lists, pricing data, and business strategies
disclosed in the course of this engagement. This obligation shall:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Survive the termination of this Agreement for a period of \textbf{three~(3)~years}
  \item Not apply to information that is publicly available through no fault of the
        receiving party
  \item Not restrict either party from disclosures required by law or court order
\end{itemize}

%% ── Section 7 ─────────────────────────────────────────────────────────────────
\section{Ownership of Work Product}

All deliverables, reports, materials, and work product specifically prepared by
Consultant for Company under this Agreement shall, upon full payment of the
applicable invoiced hours, be owned by Company. Consultant retains ownership of
its pre-existing methodologies, templates, frameworks, and general know-how, and
nothing in this Agreement shall be construed as a transfer of such pre-existing
intellectual property.

%% ── Section 8 ─────────────────────────────────────────────────────────────────
\section{Governing Law}

This Agreement shall be governed by and construed in accordance with applicable
laws as agreed upon by both parties. Any disputes arising under this Agreement that
cannot be resolved through good-faith negotiation shall be submitted to binding
arbitration before commencing litigation.

%% ── Signature Block ───────────────────────────────────────────────────────────
\vspace{28pt}

\begin{center}
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}\\[6pt]
  {\sffamily\bfseries\color{TPDark}IN WITNESS WHEREOF}\\[4pt]
  {\sffamily\small\color{TPGray}the parties have executed this Agreement as of the date first written above.}\\[6pt]
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}
\end{center}

\vspace{20pt}

\noindent
\signatureblock{ToosPoint Consulting}{Consultant}
\hfill
\signatureblock{iCall International}{Company}

\vspace{32pt}

\begin{mdframed}[
  linecolor=TPBorder,
  linewidth=1pt,
  roundcorner=4pt,
  backgroundcolor=TPLight,
  innerleftmargin=14pt,
  innerrightmargin=14pt,
  innertopmargin=10pt,
  innerbottommargin=10pt
]
\sffamily\footnotesize\color{TPGray}
\textbf{CONFIDENTIALITY NOTICE:} This document contains confidential and proprietary
information belonging to ToosPoint Consulting and iCall International. Unauthorized
disclosure, copying, or distribution of this document or the information contained herein
is strictly prohibited.
\end{mdframed}

\end{document}
