\documentclass{toospoint}

\begin{document}

%% ── Cover Page ────────────────────────────────────────────────────────────────
\contracttitle
  {CONSULTING AGREEMENT}
  {ToosPoint Consulting \quad×\quad Simplified Group BPO LLC}
  {\today}

%% ── Preamble ──────────────────────────────────────────────────────────────────
\begin{clausebox}
\sffamily\small
This \textbf{Consulting Agreement} (the ``Agreement'') is entered into between
\textbf{ToosPoint Consulting} (``Consultant'') and \textbf{Simplified Group BPO LLC}
(``Company''). The parties agree to the terms and conditions set forth herein.
\end{clausebox}

\vspace{10pt}

%% ── Section 1 ─────────────────────────────────────────────────────────────────
\section{Scope of Services}

Consultant will provide services related to the following areas on behalf of the Company:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Direct client acquisition and pipeline development
  \item Sales strategy design and execution
  \item Outreach programs and campaign management
  \item RFP identification, preparation, and submission
  \item Related consulting and execution support as mutually agreed
\end{itemize}

%% ── Section 2 ─────────────────────────────────────────────────────────────────
\section{Compensation}

Company agrees to pay Consultant a \textbf{monthly retainer of \$4,000 USD} for a
minimum commitment of \textbf{40+ hours per month}. Payment is due \textbf{Net~15}
from the invoice date.

\begin{clausebox}
\sffamily\footnotesize\color{TPGray}
\textbf{Note:} Invoices are issued at the beginning of each month and payable Net~15.
\end{clausebox}

%% ── Section 3 ─────────────────────────────────────────────────────────────────
\section{Commission}

Consultant will receive a \textbf{10\% commission} on all net new revenue generated
from clients introduced, influenced, or closed through Consultant's efforts, whether
directly or indirectly.

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Commission will be paid for a period of \textbf{18~months per client}
  \item The commission period begins on the date of first revenue collection from
        the applicable client
  \item Commission obligations apply regardless of whether this Agreement remains
        active during the 18-month period
\end{itemize}

\vspace{4pt}
\noindent\textbf{Commission Term.} Commission for each applicable client shall be
payable for a period of \textbf{eighteen~(18)~months} from the date of first revenue
collection from such client, or until the final month in which revenue is received
from that client, whichever occurs first.

%% ── Section 4 ─────────────────────────────────────────────────────────────────
\section{Definition of Net New Client}

A \textbf{net new client} is defined as any client not actively engaged with the
Company at the start of this Agreement, where active engagement is defined as
generating revenue within the \textbf{six~(6) months prior to the Effective Date}.

%% ── Section 5 ─────────────────────────────────────────────────────────────────
\section{Commission Payment Terms}

Commission shall be calculated based on \textbf{revenue actually collected} by the
Company from qualifying clients and paid \textbf{monthly}. Specifically, commission
will be calculated based on \textbf{client billings minus interpreter/vendor payouts},
excluding internal overhead, administrative costs, or discretionary expense
allocations. A commission statement detailing the clients, revenue collected, and
commission owed shall accompany each payment. Disputes must be raised within
30~days of statement delivery.

%% ── Section 6 ─────────────────────────────────────────────────────────────────
\section{Term and Termination}

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item This Agreement will begin on the agreed effective date and continue on a
        \textbf{month-to-month} basis until terminated.
  \item Either party may terminate this Agreement with \textbf{30~days written notice}.
  \item \textbf{Commission obligations survive termination} for all clients introduced
        or closed prior to termination, for the full 18-month commission period
        applicable to each such client.
  \item Retainer obligations cease as of the effective termination date.
\end{itemize}

%% ── Section 7 ─────────────────────────────────────────────────────────────────
\section{Independent Contractor}

Consultant is an \textbf{independent contractor} and not an employee, agent, or
partner of the Company. Consultant retains sole responsibility for all taxes, benefits,
and obligations arising from Consultant's business operations. Nothing in this Agreement
shall be construed to create an employment, partnership, or joint-venture relationship.

%% ── Section 8 ─────────────────────────────────────────────────────────────────
\section{Confidentiality}

Both parties agree to maintain the confidentiality of each other's proprietary
information, trade secrets, client lists, pricing data, and business strategies
disclosed in the course of this engagement. This obligation shall:

\begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=4pt]
  \item Survive the termination of this Agreement for a period of \textbf{three~(3)~years}
  \item Not apply to information that is publicly available through no fault of the
        receiving party
  \item Not restrict either party from disclosures required by law or court order
\end{itemize}

%% ── Section 9 ─────────────────────────────────────────────────────────────────
\section{Non-Circumvention}

Company agrees not to circumvent Consultant by engaging directly with clients
introduced by Consultant for the purpose of avoiding commission obligations. Any
direct engagement with such clients — whether for the same or similar services —
shall be deemed subject to the commission terms set forth in this Agreement for the
full applicable 18-month period.

%% ── Section 10 ────────────────────────────────────────────────────────────────
\section{Governing Law}

This Agreement shall be governed by and construed in accordance with applicable
laws as agreed upon by both parties. Any disputes arising under this Agreement that
cannot be resolved through good-faith negotiation shall be submitted to binding
arbitration before commencing litigation.

%% ── Signature Block ───────────────────────────────────────────────────────────
\vspace{28pt}

\begin{center}
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}\\[6pt]
  {\sffamily\bfseries\color{TPDark}IN WITNESS WHEREOF}\\[4pt]
  {\sffamily\small\color{TPGray}the parties have executed this Agreement as of the date first written above.}\\[6pt]
  {\color{TPBorder}\rule{0.7\textwidth}{0.5pt}}
\end{center}

\vspace{20pt}

\noindent
\signatureblock{ToosPoint Consulting}{Consultant}
\hfill
\signatureblock{Simplified Group BPO LLC}{Company}

\vspace{32pt}

\begin{mdframed}[
  linecolor=TPBorder,
  linewidth=1pt,
  roundcorner=4pt,
  backgroundcolor=TPLight,
  innerleftmargin=14pt,
  innerrightmargin=14pt,
  innertopmargin=10pt,
  innerbottommargin=10pt
]
\sffamily\footnotesize\color{TPGray}
\textbf{CONFIDENTIALITY NOTICE:} This document contains confidential and proprietary
information belonging to ToosPoint Consulting and Simplified Group BPO LLC. Unauthorized
disclosure, copying, or distribution of this document or the information contained herein
is strictly prohibited.
\end{mdframed}

\end{document}
