\documentclass{toospoint}

\hypersetup{
  pdftitle={Non-Disclosure Agreement},
  pdfauthor={ToosPoint Consulting}
}

\usepackage{geometry}
\geometry{top=1in, bottom=0.55in, left=0.9in, right=0.9in,
          headheight=50pt, headsep=18pt, footskip=22pt}

\titleformat{\section}[block]
  {\sffamily\bfseries\normalsize\color{TPDark}}
  {\textcolor{TPTeal}{\thesection.}}
  {0.5em}
  {}
\titlespacing*{\section}{0pt}{8pt}{2pt}

\begin{document}

\fancyhead[C]{%
  \sffamily\small\color{TPGray}%
  \textbf{\color{TPDark}NON-DISCLOSURE AGREEMENT}\\[2pt]
  \textcolor{TPTeal}{ToosPoint Consulting}\;\textcolor{TPGray}{×}\;Simplified Group BPO LLC%
}

\thispagestyle{fancy}

\vspace{4pt}
{\color{TPOrange}\rule{\linewidth}{1pt}}
\vspace{6pt}

%% ── Preamble ──────────────────────────────────────────────────────────────────
{\sffamily\footnotesize\noindent
This \textbf{Non-Disclosure Agreement} (the ``Agreement'') is entered into between
\textbf{ToosPoint Consulting} and \textbf{Simplified Group BPO LLC} (each a
``Party''), who may disclose confidential information to one another in connection
with a contemplated or ongoing business relationship.\par}

\small

\section{Confidential Information}
\noindent``\textbf{Confidential Information}'' means any non-public information disclosed
by one Party (``Disclosing Party'') to the other (``Receiving Party''), orally, in
writing, or electronically, that is marked confidential or reasonably understood
to be so, including business plans, financials, pricing, client/vendor/interpreter
lists and payout structures, trade secrets, methodologies, and proprietary know-how.

\section{Obligations}
\noindent Each Receiving Party shall (a)~hold Confidential Information in strict confidence
using at least a reasonable standard of care; (b)~use it solely to evaluate or
conduct the business relationship; (c)~limit access to personnel with a need to
know who are bound by equivalent confidentiality obligations; and (d)~not disclose,
copy, reverse-engineer, or distribute it to any third party without the Disclosing
Party's prior written consent.

\section{Exclusions}
\noindent Obligations do not apply to information that is (a)~already rightfully known
without confidentiality obligation, (b)~publicly available through no breach
hereof, (c)~rightfully received from a third party without restriction, or
(d)~independently developed without reference to the Disclosing Party's
Confidential Information. Legally compelled disclosures are permitted with prompt
written notice where lawful.

\section{Non-Circumvention}
\noindent Neither Party shall use the other's Confidential Information to solicit or
transact directly with any client, prospect, vendor, or interpreter introduced by
the other Party for the purpose of circumventing that Party, during the term and
for \textbf{twelve~(12)~months} thereafter.

\section{Term, Return \& Remedies}
\noindent This Agreement is effective for \textbf{two~(2)~years}; confidentiality
obligations survive for \textbf{three~(3)~years} from disclosure. Upon request or
termination, the Receiving Party shall promptly return or destroy all Confidential
Information. All Confidential Information remains the sole property of the
Disclosing Party; no license is granted. Each Party acknowledges that breach may
cause irreparable harm entitling the Disclosing Party to \textbf{injunctive
relief} in addition to other remedies. Governed by applicable laws as mutually
agreed; may be executed in counterparts, including by electronic signature.

\normalsize

%% ── Signature Block ───────────────────────────────────────────────────────────
\vspace{8pt}

\begin{center}
  {\sffamily\footnotesize\bfseries\color{TPDark}IN WITNESS WHEREOF}\enspace%
  {\sffamily\scriptsize\color{TPGray}the Parties have executed this Agreement as of the Effective Date.}
\end{center}

\vspace{4pt}

\noindent
\begin{minipage}[t]{0.46\textwidth}
  \sffamily\footnotesize
  {\color{TPGray}ToosPoint Consulting}\\[22pt]
  {\color{TPDark}\rule{\linewidth}{0.6pt}}\\[1pt]
  {\color{TPGray}Authorized Signature \; · \; Date}\\[14pt]
  {\color{TPBorder}\rule{\linewidth}{0.6pt}}\\[1pt]
  {\color{TPGray}Printed Name \; · \; Title}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.46\textwidth}
  \sffamily\footnotesize
  {\color{TPGray}Simplified Group BPO LLC}\\[22pt]
  {\color{TPDark}\rule{\linewidth}{0.6pt}}\\[1pt]
  {\color{TPGray}Authorized Signature \; · \; Date}\\[14pt]
  {\color{TPBorder}\rule{\linewidth}{0.6pt}}\\[1pt]
  {\color{TPGray}Printed Name \; · \; Title}
\end{minipage}

\end{document}
